Testing gene methylation enrichment analysis approaches using simulated data - summarise data

### 2023-11-03 figs/GSE158422_simulate_summary.Rmd
summary

```{r,summary,fig.width=10,fig.height=4}

@@

@@

barplot(t(x),beside=TRUE,ylim=c(0,1.2),ylab="index", legend = colnames(x) ,main="20 genes per set")
grid()

@@

barplot(t(x),beside=TRUE,ylim=c(0,1.2),ylab="index", legend = colnames(x) ,main="50 genes per set")
grid()

@@

barplot(t(x),beside=TRUE,ylim=c(0,1.2),ylab="index", legend = colnames(x) ,main="100 genes per set")
grid()

>>>>

```{r,summary,fig.width=12,fig.height=3}

@@

mar = c(5.1, 4.1, 5.1, 2.1)

@@

cols <- c("white","gray","black")

barplot(t(x),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, main="20 genes per set")
grid()

legend("topleft", inset=.1, c("Precision","Recall","F1"), fill=cols, cex=0.8)

@@

barplot(t(x),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, main="50 genes per set")
grid()

@@

barplot(t(x),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, main="100 genes per set")
grid()
